---
title: "MD1 - breed figure"
output: html_document
---

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(phytools)
library(here)
library(plotrix)
library(RColorBrewer)
```
## Preregistered data

### Read data

```{r loading data}
prereg.data <- read.csv(here('data','md1_data_vienna_long.csv')) %>%
  filter(preregistered_data=='after_prereg') #only data that were collected after preregistration
  
```

### Aggregate breed level data
```{r, message = FALSE}
breed.means <- prereg.data %>%
  filter(condition != "odour", condition != "w_2cp_vd") %>% #only test conditions
  group_by(subject_ID, breed, condition) %>%
  summarise(mean.resp = mean(response)) %>%
  ungroup() %>%
  group_by(condition, breed) %>%
  summarise(mean = mean(mean.resp, na.rm = T), sem = std.error(mean.resp, na.rm = T)) %>%
  pivot_wider(id_cols = breed, names_from = condition, values_from = c(mean, sem))

```

### Load cladogram file and align names for plot
White Swiss Shepherd Dogs descend from white colored GSD and for purposes of the cladogram will be treated as GSD

```{r, message = FALSE}
load(here('data','dog_tree.RData')) #cladogram
my.names <- read_csv(here('data','tree_names.csv'))
# Obnoxiously for some of the plot functions I can't have spaces in the names
my.names$tree.name <- gsub(" ", "_", my.names$tree.name)
dog.tree$tip.label <- gsub(" ", "_", dog.tree$tip.label)
breed.means$tip <- my.names$tree.name[match(breed.means$breed, my.names$data.name)]
to.drop <- c(setdiff(breed.means$tip, dog.tree$tip.label), setdiff(dog.tree$tip.label, breed.means$tip))
dog.tree <- drop.tip(dog.tree, to.drop)
dog.tree <- compute.brlen(dog.tree, 1)
breed.means <- breed.means[!breed.means$tip %in% to.drop,]
# align order
breed.means <- breed.means[match(dog.tree$tip.label, breed.means$tip),]
```

### Make plots on tree
Here's a barplot option.  Getting error bars is not easy and i can spend some time trying to figure it out if people like this approach
```{r, message = FALSE, results = 'hide'}
plot.data <- breed.means %>% select(mean_non, mean_ost, tip) %>% column_to_rownames(var = "tip") %>% rename(ostensive = mean_ost, nonostensive = mean_non) %>% as.matrix()
dog.chronos <- chronos(dog.tree)
plotTree.barplot(dog.chronos, plot.data, args.barplot = list(beside=TRUE, space = c(0,1.2), col = c('blue', 'red'), legend.text = TRUE,args.legend = list(x = 0.65, y = 33, bty = 'n', horiz = T)))

```

Or alternatively, here is a heatmap

```{r}
my.colors = colorRampPalette(brewer.pal(9,"YlOrRd"))(500)
phylo.heatmap(dog.tree, plot.data, split = c(0.5,0.3), fsize = c(1,1,0.75), colors = my.colors, grid = T, xlim = c(-0.5,1.5), ylim = c(-0.25,1.4), mar = c(1,1,1,1), standardize = F)
```





